Sparse Function-space Representation \\ of Neural Networks

### 2023-08-04 paper/main.tex
moved the rl related work section to the appendix

\textbf{Uncertainty quantification in RL}
A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
%That is, should an agent select actions that it knows will lead to high reward %(exploitation), or should it
%select new ones in hope to discover actions leading to higher reward (exploration).
One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL) \cite{dearden1999model,osbandMoreEfficientReinforcement2013},
and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020,jaksch2010near}.
No single strategy has emerged as a go-to method and we highlight that these strategies are only as good as their uncertainty estimates.
Previous approaches have used GPs \cite{deisenroth2011pilco,kamtheDataEfficient2018},
ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
and variational inference \cite{galImproving2016,houthooftVIME2017}.
However, each method has its pros and cons.
In this paper, we present a method which combines some of the pros from NNs with the benefits of GPs.

@@

>>>>

%\textbf{Uncertainty quantification in RL}
%A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
%%That is, should an agent select actions that it knows will lead to high reward %(exploitation), or should it
%%select new ones in hope to discover actions leading to higher reward (exploration).
%One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
%Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
%sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL) \cite{dearden1999model,osbandMoreEfficientReinforcement2013},
%and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020,jaksch2010near}.
%No single strategy has emerged as a go-to method and we highlight that these strategies are only as good as their uncertainty estimates.
%Previous approaches have used GPs \cite{deisenroth2011pilco,kamtheDataEfficient2018},
%ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
%and variational inference \cite{galImproving2016,houthooftVIME2017}.
%However, each method has its pros and cons.
%In this paper, we present a method which combines some of the pros from NNs with the benefits of GPs.

@@

\subsection{Uncertainty quantification in RL}
A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
%That is, should an agent select actions that it knows will lead to high reward %(exploitation), or should it
%select new ones in hope to discover actions leading to higher reward (exploration).
One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL) \cite{dearden1999model,osbandMoreEfficientReinforcement2013},
and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020,jaksch2010near}.
No single strategy has emerged as a go-to method and we highlight that these strategies are only as good as their uncertainty estimates.
Previous approaches have used GPs \cite{deisenroth2011pilco,kamtheDataEfficient2018},
ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
and variational inference \cite{galImproving2016,houthooftVIME2017}.
However, each method has its pros and cons.
In this paper, we present a method which combines some of the pros from NNs with the benefits of GPs.
